The pollination trade-off

### 2018-02-27 publication/supp_info.Rmd
Move figures and tables arround to match order of manuscript references

---
title: "Supplementary materials"
author: "Fernando Cagua"
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
---

@@

@@

```{r fig-conspecific-per-site, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different communities. Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio."}
loadd(dep_frame, sites)
site_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>%
  mutate(pollen_category = paste(pollen_category, "pollen"), 
         treatment = if_else(treatment == 'closed', 'bagged', treatment)) %>% 
  plyr::dlply('site_name', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = recipient_short,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() + 
      ggtitle(paste(x$locality[1], '-', x$land_use, x$fragment)) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Blues")
  })

@@

```{r fig-conspecific-per-plant, fig.height = 7, fig.cap="Conspecific pollen density across communities for different study species. Only species present in more than onse site are shown. Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio; A, and R indicate that the community corresponded to an agricultural or reserve site respectively."}
loadd(dep_frame, sites)
plant_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>%
  mutate(pollen_category = paste(pollen_category, "pollen"), 
         treatment = if_else(treatment == 'closed', 'bagged', treatment)) %>%
  group_by(recipient) %>%
  mutate(n_sites = n_distinct(site_name), 
         site_name = `str_sub<-`(site_name, 1, 3, value = ''), 
         site_name = str_replace_all(site_name, '_', ' - ')) %>%
  group_by() %>%
  filter(n_sites >= 2) %>%
  plyr::dlply('recipient', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = site_name,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() +
      ggtitle(paste(x$recipient[1])) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Blues")
  })

@@

```{r fig-deposition-logtransformed-or-not, fig.height = 2.5, fig.cap = "Distribution of stigmatic pollen density plotted in (A) a linear scale, and (B) a logarithmic scale (zero values not shown)."}
loadd(dep_frame, sites)

p1 <- dep_frame %>%
  mutate(pollen_category = paste(pollen_category, "pollen"), 
         treatment = if_else(treatment == 'closed', 'bagged', treatment)) %>%
  ggplot(aes(x = pollen_density, colour = treatment)) + 
  stat_density(geom = "line") +
  facet_wrap( ~ pollen_category, scales = "free") +
  pub_theme() +
  scale_color_brewer(palette = "Blues") +
  labs(x = "pollen density (grains per stigma)", 
       colour = "flower treatment") +
  theme(legend.position = "top")

```{r fig-abundance-logtransformed-or-not, fig.height = 2.5, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
loadd(plant_rel_abu, sites)

p1 <- plant_rel_abu %>%
  filter(scale == 'community', 
         var_trans == 'log') %>%
  inner_join(sites, by = 'site_name') %>%
  ggplot() +
  stat_density(aes(x = rab, colour = locality_name),
               position = position_identity(), geom = 'line') +
  # stat_density(aes(x = abu_tot_rel_log), geom = 'line') +
  scale_color_brewer(palette = "Blues") +
  pub_theme() +
  # guides(colour = guide_legend(title = 'locality'), linetype = guide_legend(title = 'land use')) +
  labs(colour = 'locality', x = 'relative abundance')

p2 <- plant_rel_abu %>%
  filter(scale == 'global', 
         var_trans == 'log') %>%
  distinct() %>%
  inner_join(sites, by = 'site_name') %>%
  ggplot(aes(x = abu)) +
  stat_density(position = position_identity(), geom = 'line') +
  scale_color_brewer(palette = "Blues") +
  pub_theme() +
  labs(x = 'abundance (floral units)')

cowplot::plot_grid(p2, p1, rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)
```{r table-global-vs-community-models, results = 'asis'}
loadd(wilcox_glo_com)

>>>>

---
title: "The pollination trade-off"
subtitle: "Supplementary materials"
author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
documentclass: book
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
---

@@

```{r fig-deposition-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of stigmatic pollen density plotted in (A) a linear scale, and (B) a logarithmic scale (zero values not shown)."}
loadd(dep_frame, sites)

p1 <- dep_frame %>%
  mutate(pollen_category = paste(pollen_category, "pollen"), 
         treatment = if_else(treatment == 'closed', 'bagged', treatment)) %>%
  ggplot(aes(x = pollen_density, colour = treatment)) + 
  stat_density(geom = "line") +
  facet_wrap( ~ pollen_category, scales = "free") +
  pub_theme() +
  scale_color_brewer(palette = "Set1") +
  labs(x = "pollen density (grains per stigma)", 
       colour = "flower treatment") +
  theme(legend.position = "top")

```{r fig-deposition-gain-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of the difference on stigmatic pollen density between open and closed flowers for one of the bootstrap replicates used in the model sets. When (A) using directly the gain in pollen density and (B) when pollen density is log transormed prior to calculating the gain. "}
loadd(rep_1)

plot_dist <- function(fun){
    rep_1 %>%
      filter(scale == 'global', 
             var_trans == 'lin') %>%
      mutate_at(c('open', 'closed'), fun) %>% 
      ggplot(aes(x = open - closed, colour = pollen_category)) +
      stat_density(position = position_identity(), geom = "line") +
      pub_theme() +
      scale_color_brewer(palette = "Set1") +
    theme(legend.position = "top") + 
    labs(x = "gain in pollen density (open-closed)", 
         colour = "pollen type")
}

p <- list(function(x) exp(x)-1, I) %>%
  plyr::llply(plot_dist)

leg <- cowplot::get_legend(p[[1]])
cowplot::plot_grid(remove_legend(p[[1]]), remove_legend(p[[2]]), 
                   labels = LETTERS[1:2], 
                   label_size = 8,
                   ncol = 2) %>%
  cowplot::plot_grid(leg, ., rel_heights = c(0.1, 0.9), ncol = 1)
```

```{r fig-abundance-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
loadd(plant_rel_abu, sites)

p1 <- plant_rel_abu %>%
  filter(scale == 'community', 
         var_trans == 'log') %>%
  inner_join(sites, by = 'site_name') %>%
  ggplot() +
  stat_density(aes(x = rab, colour = locality_name),
               position = position_identity(), geom = 'line') +
  # stat_density(aes(x = abu_tot_rel_log), geom = 'line') +
  scale_color_brewer(palette = "Set1") +
  pub_theme() +
  # guides(colour = guide_legend(title = 'locality'), linetype = guide_legend(title = 'land use')) +
  labs(colour = 'locality', x = 'relative abundance')

p2 <- plant_rel_abu %>%
  filter(scale == 'global', 
         var_trans == 'log') %>%
  distinct() %>%
  inner_join(sites, by = 'site_name') %>%
  ggplot(aes(x = abu)) +
  stat_density(position = position_identity(), geom = 'line') +
  scale_color_brewer(palette = "Set1") +
  pub_theme() +
  labs(x = 'abundance (floral units)')

cowplot::plot_grid(p2, p1, rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)
```

@@

```{r fig-conspecific-per-site, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different communities. Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio."}
loadd(dep_frame, sites)
site_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>%
  mutate(pollen_category = paste(pollen_category, "pollen"), 
         treatment = if_else(treatment == 'closed', 'bagged', treatment)) %>% 
  plyr::dlply('site_name', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = recipient_short,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() + 
      ggtitle(paste(x$locality[1], '-', x$land_use, x$fragment)) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Set1")
  })

@@

```{r fig-conspecific-per-plant, fig.height = 7, fig.cap="Conspecific pollen density across communities for different study species. Only species present in more than onse site are shown. Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio; A, and R indicate that the community corresponded to an agricultural or reserve site respectively."}
loadd(dep_frame, sites)
plant_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>%
  mutate(pollen_category = paste(pollen_category, "pollen"), 
         treatment = if_else(treatment == 'closed', 'bagged', treatment)) %>%
  group_by(recipient) %>%
  mutate(n_sites = n_distinct(site_name), 
         site_name = `str_sub<-`(site_name, 1, 3, value = ''), 
         site_name = str_replace_all(site_name, '_', ' - ')) %>%
  group_by() %>%
  filter(n_sites >= 2) %>%
  plyr::dlply('recipient', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = site_name,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() +
      ggtitle(paste(x$recipient[1])) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Set1")
  })

@@

```{r fig-model-results, fig.height = 3, fig.cap = "Model coefficients"}
loadd(tidied_fixed)

tidied_fixed %>%
  filter(term != "(Intercept)" #, 
         # var_trans == 'log'
         ) %>%
  group_by(pollen_category,scale, model, var_trans, term) %>%
  summarise(estimate = first(estimate)) %>%
  group_by() %>%
  humanize() %>%
  ggplot(aes(x = estimate, 
             colour = pollen_category)) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
  geom_freqpoly(# alpha = 0.25,
               position = position_identity(),
               draw_quantiles = c(0.5, 0.95, 0.05), 
               trim = F, 
               scale = "count",
               binwidth = 0.05, 
               geom = "line") +
  pub_theme() +
  facet_grid(scale ~ term + var_trans, scales = "free_x") +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

```{r fig-random-intercepts, fig.height= 3, fig.cap = "Random effect intercepts"}
loadd(tidied_fixed, sites)

tidied_fixed %>%
  separate("level", c("site_name", "plant_name"), sep = "/", remove = F) %>%
  filter(term == "(Intercept)" ,
         var_trans == 'log',
         scale == "community", 
         pollen_category == 'heterospecific'
         ) %>%
  humanize(sites) %>%
  ggplot(aes(x = estimate, colour = plant_name, group = level)) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
  geom_freqpoly(size = 0.25) +
  facet_grid(locality_name + fragment ~ land_use) +
  pub_theme() +
  theme(legend.position = 'none')
```

```{r table-aic-random-models, results= 'asis'}
loadd(glanced_random)

summ <- glanced_random %>%
  filter(var_trans == "log") %>%
  group_by(pollen_category, scale, var_trans, model) %>%
  mutate(delta_AIC = AIC - min(AIC)) %>%
  group_by(pollen_category, scale, var_trans, random_effect) %>%
  summarise(AIC_50 = median(delta_AIC), 
            AIC_05 = quantile(delta_AIC, 0.05),
            AIC_95 = quantile(delta_AIC, 0.95)) %>% 
  mutate_if(is.numeric, round, digits = 1) %>% 
  mutate(delta_AIC = paste0(AIC_50, " [", AIC_05, ", ", AIC_95, "]")) %>%
  group_by() %>%
  humanize() %>%
  arrange(pollen_category, scale, random_effect) %>%
  rename(`pollen category` = pollen_category, 
         `random structure` = random_effect)

contingency_table <- summ %>%
  # select(-var_trans) %>%
  ftable(row.vars = 4, col.vars = c(1, 2))

contingency_table[1:nrow(summ)] <- summ$delta_AIC

xtableFtable(contingency_table, method = "col.compact", 
             caption = paste('Comparison of the different random structures we considered. The table shows median delta AIC values of', n_distinct(glanced_random$model), "bootsrap resamples of the data. The 5th and 95th percentile are shown inside square brackets. Communities are defined by individual fragments but ignore the hierarchical arrangement of sampling sites."), 
         label = 'tab:table-aic-random-models')
```

```{r table-global-vs-community-models, results = 'asis'}
loadd(wilcox_glo_com)
